---
title: "HW 1 - Extra Credit"
author: "Cade H. Petersen"
date: "2022-09-28"
output: pdf_document
---

# 1. Install the epitools package, the load the epitools library. Then read in the dataset oswego.

```{r Problem-1, include=TRUE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(epitools)
library(readr)

   ### Importing the data set from my personal drive using readr.
homework_1_oswego <- read_csv("C:/Users/cadep/Desktop/R Files/Survey Files/R Files/Homework/homework_1_oswego.csv")

View(homework_1_oswego)
```

# 2. Create a series of fourfold plots for each food type and ill (our outcome) to discover the food that made everyone sick.

```{r Problem-2, include=TRUE, echo=TRUE}
# 2. Create a series of fourfold plots for each food type and ill (our outcome)
#  to discover the food that made everyone sick.

df <- homework_1_oswego  
   ## Made a copy in case I mess up..
colnames(df)
   # We have 11 "food types". I am not considering drinks as food types, 
     # I apologize if this is misinterpreted!
str(df) 
   ### Mmmk, all are characters, which makes sense as this is binomial type of
    ### problem..


fourfoldplot(with(df, table(ill, baked.ham))) 
   ## 29 yes, 17 no for who ate it.

fourfoldplot(with(df, table(ill, spinach)))
   ## 26 yes, 17 no for who ate it.

fourfoldplot(with(df, table(ill, mashed.potato)))
   ## 23 yes, 14 no for who ate it.

fourfoldplot(with(df, table(ill, cabbage.salad))) 
   ## 18 yes, 10 no for who ate it.

fourfoldplot(with(df, table(ill, jello))) 
   ## 16 yes, 7 no for who ate it.

fourfoldplot(with(df, table(ill, rolls))) 
   ## 21 yes, 16 no for who ate it.

fourfoldplot(with(df, table(ill, brown.bread)))
   ## 18 yes, 9 no for who ate it.

fourfoldplot(with(df, table(ill, cakes))) 
   ## 27 yes, 13 no for who ate it.

fourfoldplot(with(df, table(ill, vanilla.ice.cream)))
   ## 43 yes, 11 no for who ate it.
 #  Who can resist vanilla ice cream... based on the plots, this is our culprit!

fourfoldplot(with(df, table(ill, chocolate.ice.cream))) 
   ## 25 yes, 22 no for who ate it.

fourfoldplot(with(df, table(ill, fruit.salad))) 
   ## 4 yes, 2 no for who ate it
   ### Let's be real, are we surprised this many people didn't eat this??
```

# 3. When you find the culprit run a chi.square test on with ill as your outcome.

```{r Problem-3, echo=TRUE,include=TRUE}
chisq.test(df$ill, df$vanilla.ice.cream)
   ## Well, we can say that since our p-value > .05 that we fail to reject the 
     ## null hypothesis. Where our H0: Vanilla ice cream is suspected to have
     ## caused the food poisoning. 
```

Note that the `echo = TRUE` parameter was added to the code chunk to not-prevent printing of the R code that generated the plot for the purpose of grading.
